Sample-Efficient Reinforcement Learning \\ with Implicitly Quantized Representations

### 2024-02-02 paper/main.tex
Fig. 1
Minor updates to appendix
Code mentioned

  % Draw nodes
  \node[blob] (z0) at (0\nodedist,0) {$\vz_{\sub}$};
  \node[blob] (z1) at (1\nodedist,0) {$\hat\vz_{\subs{1}}$};
  \node[blob] (z2) at (2\nodedist,0) {$\hat\vz_{\subs{2}}$};

@@

\textbf{Limitations and Future work}
To the best of our knowledge, we are the first to present a method that learns a task-agnostic representation
using only latent-state consistency. As such, we hope our method for learning task-agnostic representations paves the
way for more research in multi-task and lifelong learning.
Given that our method obtains an implicit codebook an obvious future direction is exploring if we can leverage the
discretized latent-space. So far, we have only applied our representation learning loss to state-based tasks. Extending the method to handle even higher-dimensional visual tasks is an interesting direction. Furthermore, we have neither analyzed the scaling behavior of our world models nor how well \our performs in a multi-task setting. Utilizing the knowledge learned during with Internet-scale pre-training with large robotic datasets could make our method even more sample efficient. Exploring whether explicitly quantifying the model uncertainty by \eg\ using larger ensembles would help to adapt our method to a real-world robotics setting is also a promising direction for future work.

@@

\section{Hyperparameters}
\cref{tab:hyperparameters} lists all of the hyperparameters for training \our.
For further details please check the code which is available in the submitted supplementary material and will be made public upon acceptance.

>>>>

  % Draw nodes
  \node[blob] (z0) at (0\nodedist,0) {$\vz_{\sub}\vphantom{\hat\vz_{\subs{1}}}$};
  \node[blob] (z1) at (1\nodedist,0) {$\hat\vz_{\subs{1}}$};
  \node[blob] (z2) at (2\nodedist,0) {$\hat\vz_{\subs{2}}$};

@@

\textbf{Limitations and future work}
To the best of our knowledge, we are the first to present a method that learns a task-agnostic representation
using only latent-state consistency. As such, we hope our method for learning task-agnostic representations paves the
way for more research in multi-task and lifelong learning.
Given that our method obtains an implicit codebook an obvious future direction is exploring if we can leverage the
discretized latent-space. So far, we have only applied our representation learning loss to state-based tasks. Extending the method to handle even higher-dimensional visual tasks is an interesting direction. Furthermore, we have neither analyzed the scaling behavior of our world models nor how well \our performs in a multi-task setting. Utilizing the knowledge learned during with Internet-scale pre-training with large robotic datasets could make our method even more sample efficient. Exploring whether explicitly quantifying the model uncertainty by \eg\ using larger ensembles would help to adapt our method to a real-world robotics setting is also a promising direction for future work.

% Arno recommends to have this here as a last thing (leaves a positive feeling)
A reference implementation of the methods and benchmarking setup will be made available on GitHub upon acceptance of the paper (see supplementary material for now).

@@

\section{Hyperparameters, Implementation, and Training Infrastructure}
\cref{tab:hyperparameters} lists all of the hyperparameters for training \our. For further details please check the code which is available in the submitted supplementary material and will be made public upon acceptance. We implemented our codebase with PyTorch and used the Adam optimizer for training the models. We used five seeds for all figures. All of our models can be trained on a single GPU. We used Nvidia A100s and AMD Instinct MI250X GPUs to run our experiments.
